\documentclass[11pt]{article}
\usepackage[top=0.8in, bottom=0.9in, left=0.9in, right=0.9in]{geometry}

\begin{document}
Solution to the problems in https://piazza.com/class/llb4bhwh59g9n/post/1039

(I'm assuming reductions are made in polynomial time.)

\begin{enumerate}
    \item ShortestPath, Primality
    \item All of them
    \item 
    \begin{enumerate}
        \item false. To be NP-complete, the problem must be in NP-hard and in NP.
        \item true. By definition (see above).
    \end{enumerate}
    \item 
    \begin{enumerate}
        \item true (it's NP-complete)
        \item false
        \item true (all NP-complete problems can be reduced to all other NP-complete problems)
        \item true (by same logic above)
    \end{enumerate}
    \item 
    \begin{enumerate}
        \item yes, A must be NP-complete, and all NP-complete problems can be reduced to all other NP-complete problems.
        \item yes by above logic.
    \end{enumerate}
    \item 
    \begin{enumerate}
        \item true. Use the reduction to transform the certificate into an instance of B, which is NP. Therefore, A is also NP.
        \item true. Reducing A to B doesn't tell if it is in P or NP-hard. (However, if we reduced B to A, we'd know A was NP-complete.)
        \item false. As explained above, this isn't necessarily true.
    \end{enumerate}
    \item Create a graph $G' = G$. Let $k' = |V| - k$. Run independent set on $G'$ and $k'$. Let $S'$ be the returned indpendent set. Then, the solution to edge-monitoring is $S = V - S'$. (Clearly, this reduction is polynomial-time.)

    Now, we prove that G' has a size-k' independent set S' IFF G has a size-k edge-monitoring set S.

    Assume, G' has a size-k' indpendent set S'.\\
    For every edge $e \in E$, $e$ cannot have both vertices in $S'$ since $S'$ is an independent set.\\
    Therefore, at least one of the vertices of $e$ must be in $S$.\\
    Therefore, $e$ is monitored.\\
    Therefore, every edge is monitored. (i.e. $S$ is a ``vertex cover'')

    Assume $G$ has a size-k solution to edge-monitoring (a ``vertex cover'') $S$.\\
    For every edge $e \in E$, $e$ must have at least one vertex in $S$ since it is covered by $S$.\\
    Therefore, $e$ does not have both vertices in $S'$.\\
    Therefore, no edge connects 2 vertices in $S'$.\\
    Therefore, $S'$ is an independent set.
\end{enumerate}
\end{document}